Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-18 Scripts/Initial_Analysis.Rmd
Ready for results

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf"))

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
            )
# warnings() for empty data species

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% 
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1)

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf"))

eez_centroid <- read_csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""))

@@

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eez_name,Tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T)) %>% 
  gather("metric","value",mean_yr:sd_yr)

@@

map <- World_eez_sf %>% 
  left_join(eez_d_hist,
            by = "eez_name") %>% 
  filter(Tresh == "Tresh_two",
         metric == "mean_yr") %>%
  ggplot() +
  geom_sf(
    aes(
      fill = value
    )
  ) +
  geom_sf(data =World_map, aes(), size = 0.1, fill = "gray90", col = "gray90") +
  scale_fill_viridis() +
  my_ggtheme_m() +
  # facet_wrap(~Tresh,
             # ncol = 1) +
  ggsave("./Figures/emer_map_T2a.png",
         width = 12,
         height = 10,
         units = "in"
  )

>>>>

results <- my_path("R",name="proportion_change_2005.csv", read=T)

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>% 
  rename(fishing_entity = name_long) %>% 
  clean_names()

@@

# Clean names to match data
matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T)

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(matching_names,
            by=  "sf_eez_name") %>% 
  clean_names()
# warnings() for empty data species

@@

# Load it!
World_eez_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  # st_transform(crs = 4326) %>% # 4326
  st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>% 
  rename(fishing_entity = name_long) %>%
  left_join(matching_names,
            by = "fishing_entity") %>% 
  distinct(fishing_entity,.keep_all = TRUE) %>% 
  st_transform(crs = "+proj=eck4") %>% # for tbular plot

# eez_centroid <- read_csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""))

@@

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eezid  = sf_eezid,fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa)

# Per fishing entity

fish_d_hist <- Eme_Res %>% 
  group_by(fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    value = length(unique(taxon_key))
    ) %>% 
  filter(!is.na(fishing_entity))

@@

World_map_nemer <- World_map %>%
  mutate(fishing_entity = ifelse(fishing_entity == "United States","USA", fishing_entity)) %>% 
  left_join(fish_d_hist,
            by = "fishing_entity")

for(i in 1:2){

  Tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_",Tresh_list[i],".png")

  map <- World_eez_sf %>% 
    left_join(eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == Tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_nemer, aes(fill = value +2000   # to match scales
                                        ),
      color =  "white",
      size = 0.1
      ) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25)
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )
